\Large{Adversarial Training against Systematic Uncertainty}

### 2016-10-25 tex/paper.tex
save

For fixed $\theta_f$, the adversary $r$ is optimal at $$\hat\theta_r = \arg
\max_{\theta_r} E(\theta_f, \theta_r)  = \arg \min_{\theta_r} {\cal
L}_r(\theta_f, \theta_r),$$ in which case $p_{\hat\theta_r}(z|f(X;\theta_f)=s) =
p(z|f(X;\theta_f)=s)$ for all $z$ and all $s$, and ${\cal L}_r$ reduces to the expected entropy
$\mathbb{E}_{s \sim f(X;\theta_f)} [ H({Z|f(X;\theta_f)=s}) ]$ of the conditional distribution of the nuisance.
This expectation is nothing else than the conditional entropy of the random variables
$Z$ and $f(X;\theta_f)$ and can be written as $H(Z|f(X;\theta_f))$.
Accordingly, the
value function $E$ can be restated as a function depending on $\theta_f$ only: $$E'(\theta_f) = {\cal
L}_f(\theta_f) -  H({Z|f(X;\theta_f)}).$$  In particular, we have the lower
bound $$H({Y|X}) - H(Z) \leq {\cal L}_f(\theta_f) - H({Z|f(X;\theta_f)})$$
where the equality holds at $\smash{\hat\theta}_f = \arg \min_{\theta_f}
E'(\theta_f)$ only when
\begin{itemize}
    \item $\smash{\hat\theta}_f$ minimizes the negative log-likelihood ${\cal
    L}_f$ of $X|Y$, which happens when $\smash{\hat\theta}_f$ are the parameters
    of an optimal classifier and in which case ${\cal L}_f$ reduces to its
    minimum value $H({Y|X})$,

>>>>

For fixed $\theta_f$, the adversary $r$ is optimal at $$\hat\theta_r = \arg
\max_{\theta_r} E(\theta_f, \theta_r)  = \arg \min_{\theta_r} {\cal
L}_r(\theta_f, \theta_r),$$ in which case $p_{\hat\theta_r}(z|f(X;\theta_f)=s) =
p(z|f(X;\theta_f)=s)$ for all $z$ and all $s$, and ${\cal L}_r$ reduces to the expected entropy
$\mathbb{E}_{s \sim f(X;\theta_f)} [ H({Z|f(X;\theta_f)=s}) ]$ of the conditional distribution of the nuisance.
This expectation is nothing else than the conditional entropy of the random variables
$Z$ and $f(X;\theta_f)$ and can be written as $H(Z|f(X;\theta_f))$.
Accordingly, the
value function $E$ can be restated as a function depending on $\theta_f$ only: $$E'(\theta_f) = {\cal
L}_f(\theta_f) -  H({Z|f(X;\theta_f)}).$$  In particular, we have the lower
bound $$H({Y|X}) - H(Z) \leq {\cal L}_f(\theta_f) - H({Z|f(X;\theta_f)})$$
where the equality holds at $\smash{\hat\theta}_f = \arg \min_{\theta_f}
E'(\theta_f)$ only when
\begin{itemize}
    \item $\smash{\hat\theta}_f$ minimizes the negative log-likelihood of $Y|X$ under $f$,
    which happens when $\smash{\hat\theta}_f$ are the parameters
    of an optimal classifier and in which case ${\cal L}_f$ reduces to its
    minimum value $H({Y|X})$,
